Predicting Covid-19 Data

### 2022-12-06 powerpoint.rmd
update pptx and rmd

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths), color = "red") +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) +
  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# extract Italy data
italy <- data %>% 
  filter(location=="Italy") %>% 
  filter(date <= "2020-04-21") %>%
  filter(date >= "2020-02-15") %>%
  select(date, total_cases, total_deaths)
  #ref: %>% mutate(days = c(1:67))
italy[45:67,] <- NA
italy <- italy %>% mutate(days = c(1:67))

@@

#plot
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases")
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#plot
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths")
```

@@

* Create a random matrix : m X n
  * m = number of random outcomes (*chosen to be 150*)
  * n = number of observed days (*n = 1,...,j*)
* Each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*

@@

## 150 Monte Carlo simulations plotted

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() +
  geom_point(aes(x=1:m, y=flex_ca), color="red") +
  geom_hline(yintercept=mean(flex_ca), color="blue") +
  labs(x = "Number of Monte Carlo simulation", y = "Day of flex, from February 15")
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#plot(cs)
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases") + 
  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1.5, linetype="dashed")
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#plot(ft)
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() +
    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths") +
  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1.5, linetype="dashed")
```

>>>>

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths)) +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) +
  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(400)
# extract Italy data
italy <- data %>% 
  filter(location=="Italy") %>% 
  filter(date <= "2020-04-21") %>%
  filter(date >= "2020-02-15") %>%
  select(date, total_cases, total_deaths)
  #ref: %>% mutate(days = c(1:67))
italy[45:67,] <- NA
italy <- italy %>% mutate(days = c(1:67))

@@

#plot
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases")
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#plot
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths")
```

@@

* Create a random matrix : m X n
  * m = number of random outcomes (*chosen to be 150*)
  * n = number of observed days (*n = 1,...,j*)
* Each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
* Each of the 150 simulations were fitted with the Gauss error function
* Then determined the date of the flex for each simulation

@@

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() +
    geom_point(aes(x=1:m, y=flex_ca), color="#d33636") +
    geom_hline(yintercept=mean(flex_ca), color="#d33636", linetype="dashed", size=1.5) + 
    labs(title = "MonteCarlo Simulation for Day of Flex (Cases)", x = "Trial", y = "Day of Flex")
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#plot(cs)
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases") + 
  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1, linetype="dashed")
```

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() +
    geom_point(aes(x=1:146, y=flex_fa), color="#1b95ff") +
    geom_hline(yintercept=mean(flex_fa), color="#1b95ff", linetype="dashed", size=1.5) + 
    labs(title = "MonteCarlo Simulation for Day of Flex (Fatalities)", x = "Trial", y = "Day of Flex")
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#plot(ft)
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() +
    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths") +
  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1, linetype="dashed")
```
